Toxic Code Snippets on Stack Overflow

### 2018-05-20 cloverflow-tse/cloverflow.tex
The complete draft of the cover letter and the TSE paper.

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Online code clones are code fragments that are copied from software projects or
online sources to Stack Overflow as examples. Due to an absence of a checking
mechanism after the code has been copied to Stack Overflow, they can become
toxic code snippets, i.e.~they suffer from being outdated or violating the
original software license. We present a study incorporating state-of-the-art
tools and techniques to automatically extract and filter online clone pairs
between 72,365 Java code snippets on Stack Overflow and 111 open source projects
in the curated Qualitas corpus. We analysed 2,289 non-trivial online clone
candidates. Our investigation revealed strong evidence that 154 clones have been
copied from a Qualitas project to Stack Overflow. We found 101 of them (66\%) to
be outdated and potentially harmful for reuse. Furthermore, we found 214 code
snippets that could potentially violate the license of their original software.
A survey of 201 high-reputation Stack Overflow answerers (33\% response rate)
showed that 131 participants (65\%) have ever been notified of outdated code and
26 of them (20\%) rarely or never fix the code. 138 answerers (69\%) never check
for licensing conflicts between their copied code snippets and Stack Overflow's
CC BY-SA 3.0.

@@

Toxic code snippets mean code snippets that, after incorporating into software,
the cost of paying back the technical debt exceeds the value it generates in the long run.
Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1)~outdated, (2)~violating their original software
license, (3) exhibiting code smells, or (4) having security vulnerabilities. 
In this study, we focus on the first two forms of toxic code snippets, outdated code and license-violating code,
as these two problems are still under explored compared to code smells~\cite{Tufano2015} and vulnerabilities~\cite{Acar2016,Fischer2017}.
Outdated code snippets can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license, e.g.\ GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting licenses, legal issues may occur.

@@

\subsection{Empirical Study of Online Code Clones}
We support the motivation and the findings in the surveys by performing
an empirical study of online code clones between Stack Overflow
answers and 111 Java open source projects.
We designed the study in 6 phases as depicted in \Cref{fig:exp_framework} where
we build different data sets to answer RQ2 to RQ5.

@@

The threshold \textit{t} is crucial for the ok-match because it affects the number
of merged clone pairs. Setting a high \textit{t} value will result in a few ok-match clone pairs
and duplicates of the same clone pairs (which are supposed to be merged) may appear in the merged
clone set. On the other hand, setting a low \textit{t} value will result in many ok-match clone
pairs and some non-duplicate clone pairs may be accidentally merged by only
a few matching lines.
In order to get an optimal $t$ value, we did an analysis by choosing
five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates.
By setting $t=0.7$ according to Bellon's study, we
found 97 ok-match pairs reported. On the other hand, setting $t$ to 0.1, 0.3,
0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually
checked all the 111 reported pairs. We found one false positive pair and 110
true positive pairs. By raising the $t$ to 0.3 and 0.5, we got rid of the false
positive pair and still retained all the 110 true positive pairs. All the clone
pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a
subset of $t=0.5$. However, since there is a fewer true positive pairs reported
(i.e.~generating false negatives), we ended up leaving some duplicates of the 
same clones in the final merged clone set.
With this analysis, we can see that setting the threshold $t$ to 0.1 is too
relaxed and results in having false positive ok-match pairs, while setting the
$t$ to 0.7 or 0.9 is too strict. Thus,
we decided to select the $t$ value at 0.5.

@@

Lastly, we searched for the outdated code snippets in 130,703 GitHub projects to
see how widespread is the outdated code in the wild. We mined GitHub
based on the number of stars the projects received, which indicated their popularity. We relied on
GitHub API to query the project metadata before cloning them.
Since GitHub API returned only top 1,000 projects at a time for each query, we formulated the
query to retrieve most starred projects based on their sizes.
The project size range started from 1KB to 2MB with 1KB step size and the last query is
for all the remaining projects that were larger than 2MB.
With this method, we retrieved the top 1,000 most starred projects for each project size. 
As a result, we cloned 130,703 GitHub projects ranging from 29,465 stars to 1 star.
A clone detection was then performed between the outdated code snippets and the GitHub
projects. We selected SourcererCC with 80\% similarity for this task because it
could scale to a large-scale data set, while Simian could not. Finally, we analysed
the clone reports and manually checked the clones.

@@

We analysed licensing conflicts of the online clones in the \textbf{QS},
\textbf{EX}, and \textbf{UD} set. The licenses were extracted by \emph{Ninka},
an automatic license identification tool~\cite{German2010}. Since Ninka works at
file level, we report the findings based on Stack Overflow snippets and Qualitas
source files instead of the clone pairs (duplicates were ignored). For the ones
that could not be automatically identified by Ninka and have been reported as
{\small\texttt{SeeFile}} or {\small\texttt{Unknown}}, we looked at them manually
to see if any license can be found. For EX clone pairs that are cloned from
external sources such as JDK or websites, we manually searched for the license
of the original code.

@@

\vspace{0.25cm}
\textit{RQ1.1 How often are Stack Overflow
	answerers aware of the outdated code and 
	licensing conflicts when
	they answer a question on Stack Overflow?} 
\vspace{0.25cm}

@@

We found that although the answerer have been notified of outdated code in their
answers, for 51.5\% of them such notifications occur very rarely (only 1--20\%
of the answers). Only 3 participants reported that they were notified in more
than 60\% of their answers. This notification to the answerer can be done by
posting comments below the answer on Stack Overflow. For example, the answerer of
the Stack Overflow question no.~10924648 posted a comment on his own answer
saying that the answer is specifically for Spring 3.1 and another user
posted a comment on the answer of the post no.~801935 that the code snippet is
not of high quality and suggested an alternative in another post.
The low percentage of outdated code notifications
reflect the experience of high reputation answerers who accumulate the reputation for a
long time. Due to the voting mechanism of Stack Overflow, high reputation users
usually provide high quality answers to earn up votes from other users. They are
careful when posting code snippets in the answer to avoid problems and, vice versa, 
getting down votes. It would be interesting to compare the findings to
Stack Overflow answerers who are newer and have lower reputation. However, we
leave it to future work.

@@

\begin{boxquote}
	To answer RQ 1.1, although most of the Stack Overflow answerers are aware that their code
	can be outdated, half of the answerers were very rarely notified of
	outdated code in the answers. After being notified, some of them rarely or never fix the outdated code.
	More than half of the answerers are aware of Stack Overflow's
	CC BY-SA 3.0 license. Only 3 answerers explicitly include software license in their answers
	while some of them choose to include the license in their profile page instead. More than half of the
	answerers never check for licensing conflicts between their copied code snippets
	and Stack Overflow's CC BY-SA 3.0.
\end{boxquote}

@@

\vspace{0.25cm}
\textit{RQ1.2 How often do Stack Overflow
	visitors experience the outdated code and licensing conflicts when
	they reuse code in an answer from Stack Overflow?}
\vspace{0.25cm}

@@

\begin{boxquote}
	To answer RQ 1.2, Stack Overflow visitors experienced several issues from Stack
Overflow answers including outdated code. The majority of them are not aware of
CC BY-SA 3.0 license enforced by Stack Overflow and never check for license
conflicts when reusing code snippets.
\end{boxquote}

@@

We performed a detailed investigation of the 100 outdated answers on Stack
Overflow two years after the snapshot we have (6 May 2018) 
on three aspects: newer or higher-voted answers and comments. We found
that there were 34 posts which contains newer answers. Regarding the number of
votes, there were 5 questions which contained answers with a higher number of
votes than the outdated answer. However, 99 of the 100 outdated answers were still
marked as accepted answers. For the comments, we check if there is any comment
to mitigate or point out the toxicity of the outdated code snippets. We found
that, out of 100 answers, there were 6 answers that had a comment saying the
code in the answer is outdated or containing issues, such as \textit{``spring
	3.1 stuff''}, \textit{``...tried this but having connect exception --
	\texttt{javax.mail.MessagingException}:\textit{ Could not connect to SMTP host:
	\texttt{smtp.gmail.com}, port: 465''}, ``You should add a \texttt{buffer.reset(null, 0, 0);} at the end of the try block to avoid excess heap usage (issue no. HADOOP-11323)''} or \textit{``.. I do not have experience
	with new versions of hibernate for a long time. But previously without clean you
	could receive some unexpected results. So I suggest to try different approaches
	or even check latest documentation''}. None of the 6 answers change their
outdated code, but the comments themselves may help to warn other Stack Overflow
users.

@@

Then, we performed the check for clones of the 100 outdated code snippets in 130,703 GitHub projects.
We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all
of them. As shown in \Cref{tab:outdated_github}, out of the 102 cloned snippets, there were
13 cloned snippets that matched with themselves because some of the Qualitas
projects also appear on GitHub. For other projects besides the Qualitas
projects, there were 47 cloned snippets that were exactly the same as the
outdated code snippets and 42 cloned snippets that were not exactly the same
(e.g.~they contained additional code modifications made by the projects'
developers or they were copied from another source with a slightly different
code).

Among the exact-copy of 47 outdated cloned snippets, there were only two cloned
snippets that gave attributions to Stack Overflow. However, the attributions
pointed to different posts than the ones we found, but containing the same code
in the answers. The other 32 cloned snippets were very likely to be a file-level
clone from its respective original project (e.g. JFreeChart, JUnit, Log4J,
Hadoop) based on their license header and the Javadoc comments. Lastly, the
remaining 13 cloned snippets did not have any hints or evidence of copying.
Twelve of them were toxic because they were the old versions that still contained bugs.

Interestingly, we discovered that the buggy version of the
\texttt{humanReadableInt()} method from Hadoop appears in two popular Java
projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854
stars and 1,946 forks). Due to the lack of evidence, we could not conclude how
this method, which is exactly the same as the toxic code snippet we found on
Stack Overflow, appears in the two projects. It is possible that the developers
retrieved them from Stack Overflow, other websites, or from Hadoop code base
directly. Nevertheless, we decided to report the developers of the two projects
regarding the issue. We created a bug report for each project (deeplearning4j
\#4694\footnote{deeplearning4j bug report:
	\url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and
HIVE-18929\footnote{Apache Hive bug report: \url{
		https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the
developers of the projects by describing the problem of race condition in the
outdated version of \texttt{humanReadableInt()} method and proposed a fix by
using the newest version of the method in Hadoop. The issue has been fixed in
deeplearning4j. The developers of deeplearning4j agreed that the method was
problematic and they decided to implement their own fix due to a concern of a
potential software licensing conflict caused by copying the fix directly from
Hadoop code base. On the other hand, the bug report in Apache Hive is still
unfixed.

The outdated online code clones cause problems ranging from uncompilable code
(due to modifications and different API usage in the outdated code) to
the introduction of vulnerabilities to the software~\cite{Xia2014}. An outdated code with a
subtle change (e.g.\ \Cref{fig:before-after}) may be copied and reused without
awareness from developers. Moreover, an outdated code with a defect (e.g.\ a race
condition problem in \Cref{fig:before-after_2}) is clearly harmful to be reused.
Stack Overflow has a voting mechanism that may mitigate this issue, the
accepted answer is still used by naive developers who copy and reuse the
outdated code.
Although we did not find strong evidence of the outdated code snippets
being cloned to GitHub projects, it would still be useful if Stack Overflow
implements a flagging of outdated answers.

\begin{boxquote}
For RQ4, our results show that 66\% (101) of QS clone pairs on Stack
Overflow are outdated. 86 pairs differ from their newest versions by
modifications applied to variable names or method names, added or deleted
statements, to a fully rewritten code with new method signatures. 15~pairs are
dead snippets. 47 outdated code snippets are found in 130,703 GitHub projects
without evidence of copying. Two of them contains a race condition and
are found in popular projects: deeplearning4j and Apache Hive.
\end{boxquote}

@@

%If developers copy and reuse these licensed pieces of code in their projects,
% conflicts may happen without their realisation.
In our study, we reveal another type of toxic code snippets which is software
licensing issues caused by code cloning to Stack Overflow. We found evidence that
154 pieces of code have been copied from Qualitas projects to Stack Overflow as
examples. Another 111 pieces of code are cloned from external sources. Their
status of accepted answers increase their chances of being reused. Even though
most of the Qualitas projects came with a software license, we found that the
license information were frequently missing after the code was copied to Stack
Overflow. The licensing terms on top of source code files are not copied because
usually only a small part of the file was cloned. In overall, we can see that
most of the Stack Overflow snippets do not contain licensing terms while their
clone counterparts in Qualitas projects and external sources do. Since licensing
statement resides on top of a file, the results here are analysed at file level,
not clone fragment, and clone pairs from the same file are merged. 
The summary of licensing information is listed in
\Cref{tab:license_abc}.

@@

The same GitHub study has been done for license-incompatible code snippets. 
We detected clones between the 214
code snippets without their original license (86 QS, 78 EX and 50 UD)  and
130,703 GitHub projects using SourcererCC with 80\% similarity threshold. Then,
we used the Ninka tool to automatically identify software license from the 7,207
code snippets. Opposite to the outdated clones, we discovered many more clones
of 7,207 candidate pairs. There were 90 pairs from 10 Qualitas projects on
GitHub and 7,117 pairs from 2,427 other projects. From
\Cref{tab:license_github}, the clones were found from highly-starred
projects (29,465 to 10 stars) to 1-star projects.
We found 12 code snippets with attributions to Stack Overflow questions/answers and
6 of them were the answers we found as clones from Qualitas or external sources.
Five code snippets did not have license while the originals had Apache-2, GPLv2,
or EPLv1 license. One snippets had AGPLv3 license while the original had Apache-2 license.
Only 995 code snippets in GitHub projects that have the same license
as the originals in Qualitas.

@@

\begin{boxquote}
For RQ5, we found 214 code snippets on Stack Overflow that
could potentially violate the license of their original software. The majority of them
do not contain licensing statements after they have been copied to
Stack Overflow. For 164 of them, we were able to identify,
with evidence, where the code snippet has been copied from.
We found 7,117 of the 214 license-incompatible code snippets
in 130,703 GitHub projects.
\end{boxquote}

@@

@@

This study empirically show from the surveys and the clone detection experiment that
online code clones occur on Stack Overflow and the clones may become toxic due
to outdated code and software license incompatibility. The findings lead to the
insight about toxicity of online code clones and two actionable items
we are proposing to the software engineering research and the Stack Overflow community.

\subsubsection{Toxicity of outdated and license-incompatible clones}
We found only a small amount of toxic outdated code snippets in open source projects on
GitHub. Besides 12 buggy and outdated code snippets found in 12 projects, the
rest were non-harmful clones of the outdated code. Although other studies show
that Stack Overflow code snippets may contain security
vulnerabilities~\cite{Acar2016,Fischer2017} or API misuse~\cite{Zhang2018}, we
found in this study that the damage caused by reusing outdated code on Stack
Overflow is not high.

On the other hand, the missing of licensing statement of online code clones on
Stack Overflow can cause more damage than outdated code. As shown in our study and
also in the study by An et al. \cite{An2017}, some online clones on Stack Overflow are
originally licensed under more restrictive license than Stack Overflow's CC
BY-SA 3.0. If these missing-license online clones are reused in a software with
incompatible license, the software owner may face legal issues. The software
auditing service such as Black Duck Software or nexB, which can effectively
check for license compliance of code copied from open source projects, cannot
check for the original license of the cloned code snippets on Stack Overflow. Although
Stack Overflow answerers participated in our survey believe that most of the
code snippets on Stack Overflow are too small to claim for copyright and they
fall under fair-use, there is still a risk due to different legal system in each
country. For example, Germany legal system does not have a concept of fair use
or the number of minimum lines of code to be consider copying, i.e.~de minimis,
is also differently interpreted from case to case or from country to country.

@@

While checking if the copied code snippets on Stack Overflow are still
up-to-date with the latest version of their originals can possibly be done
automatically, it is a challenging task to automate the process of establishing
the origin of code clones. Since automatically establishing code cloning
is still an open challenge, one viable solution for now is
encouraging the Stack Overflow developers to always include the origin of the
copied code snippet in the post so that this link is always established at the
posting time. Even better, Stack Overflow can provide an optional form to fill
in when an answerer post an answer if he or she copies code from other software
projects. The form should include the origin of the code snippet (possibly as a
GitHub url) and its original license. Using this manually established links at
posting time, we can then automate the process of checking for outdated code.

>>>>

% for Computer Society papers, we must declare the abstract and index terms
% PRIOR to the title within the \IEEEtitleabstractindextext IEEEtran
% command as these need to go into the title area created by \maketitle.
% As a general rule, do not put math, special symbols or citations
% in the abstract or keywords.
\IEEEtitleabstractindextext{%
\begin{abstract}
Online code clones are code fragments that are copied from software projects or
online sources to Stack Overflow as examples. Due to an absence of a checking
mechanism after the code has been copied to Stack Overflow, they can become
toxic code snippets, i.e.~they suffer from being outdated or violating the
original software license. We present a study of online code clones on Stack
Overflow and their toxicity by incorporating two developer surveys and a
large-scale code clone detection. A survey of 201 high-reputation Stack Overflow
answerers (33\% response rate) showed that 131 participants (65\%) have ever
been notified of outdated code and 26 of them (20\%) rarely or never fix the
code. 138 answerers (69\%) never check for licensing conflicts between their
copied code snippets and Stack Overflow's CC BY-SA 3.0. A survey of 87 Stack
Overflow visitors shows that they experienced several issues from Stack Overflow
answers: mismatched solutions, outdated solutions, incorrect solutions, and buggy code. 
85\% of them are not aware of CC BY-SA 3.0
license enforced by Stack Overflow and 66\% never check for license conflicts
when reusing code snippets. Our clone detection found online clone pairs between
72,365 Java code snippets on Stack Overflow and 111 open source projects in the
curated Qualitas corpus. We analysed 2,289 non-trivial online clone candidates.
Our investigation revealed strong evidence that 153 clones have been copied from
a Qualitas project to Stack Overflow. We found 100 of them (66\%) to be outdated
and potentially harmful for reuse. Furthermore, we found 214 code snippets that
could potentially violate the license of their original software and appear 7,112
times in 2,427 GitHub projects.

@@

Toxic code snippets mean code snippets that, after incorporating into software,
the cost of paying back the technical debt exceeds the value it generates in the long run.
Stack Overflow code snippets
cloned from open source software or online sources can become toxic when they
are (1)~outdated, (2)~violating their original software
license, (3) exhibiting code smells, or (4) having security vulnerabilities. 
In this study, we focus on the first two forms of toxic code snippets, outdated code and license-violating code,
as these two problems are still under explored compared to code smells~\cite{Tufano2015} and vulnerabilities~\cite{Acar2016,Fischer2017}.
Moreover, Stack Overflow users also express their concerns about these two problems
as shown in several discussion threads\footnote{Discussions about outdated answers and code license on
	Stack Overflow: meta.stackexchange.com/questions/131495, 
	meta.stackexchange.com/questions/11705/, meta.stackexchange.com/questions/12527,
	meta.stackexchange.com/questions/25956, meta.stackoverflow.com/questions/321291.}
	 on \textsf{meta.stackexchange.com} about outdated
answers and license of code on Stack Overflow.
Outdated code snippets can be harmful since they are not up-to-date with their originals and may
contain defects. Code snippets from open source projects usually fall under a
specific software license, e.g.\ GNU General Public License (GPL). If they are
cloned to Stack Overflow answers without the license, and then flow to other projects
with conflicting licenses, legal issues may occur.

@@

\subsection{Empirical Study of Online Code Clones}
We support the motivation and confirm the findings in the surveys by performing
an empirical study of online code clones between Stack Overflow
answers and 111 Java open source projects.
We designed the study in 6 phases as depicted in \Cref{fig:exp_framework} where
we build different data sets to answer RQ2 to RQ5.

@@

The threshold \textit{t} is crucial for the ok-match because it affects the number
of merged clone pairs. Setting a high \textit{t} value will result in a few ok-match clone pairs
and duplicates of the same clone pairs (which are supposed to be merged) may appear in the merged
clone set. On the other hand, setting a low \textit{t} value will result in many ok-match clone
pairs and some non-duplicate clone pairs may be accidentally merged by only
a few matching lines.
In order to get an optimal $t$ value, we did an analysis by choosing
five $t$ values of 0.1, 0.3, 0.5, 0.7, and 0.9 and studied the clone candidates.
By setting $t=0.7$ according to Bellon's study, we
found 97 ok-match pairs reported. On the other hand, setting $t$ to 0.1, 0.3,
0.5, and 0.9 resulted in 111, 110, 110, and 94 ok-matched pairs respectively.
Since the clone pairs of $t=0.1$ was the superset of other sets,  we manually
checked all the 111 reported pairs. We found one false positive pair and 110
true positive pairs. By raising the $t$ to 0.3 and 0.5, we got rid of the false
positive pair and still retained all the 110 true positive pairs. All the clone
pairs of $t=0.7$ (97) and $t=0.9$ (94) were also true positives due to being a
subset of $t=0.5$. However, since there is a fewer merged clone pairs, 
we ended up leaving some duplicates of the same clones in the final merged clone set.
With this analysis, we can see that setting the threshold $t$ to 0.1 is too
relaxed and results in having false positive ok-match pairs, while setting the
$t$ to 0.7 or 0.9 is too strict. Thus,
we decided to select the $t$ value at 0.5.

@@

Lastly, we searched for the outdated code snippets in 130,703 GitHub projects to
see how widespread is the outdated code in the wild. We mined GitHub
based on the number of stars the projects received, which indicated their popularity. We relied on
GitHub API to query the project metadata before cloning them.
Since GitHub API returned only top 1,000 projects at a time for each query, we formulated the
query to retrieve most starred projects based on their sizes.
The project size range started from 1KB to 2MB with 1KB step size and the last query is
for all the remaining projects that were larger than 2MB.
With this method, we retrieved the top 1,000 most starred projects for each project size. 
As a result, we cloned 130,703 GitHub projects ranging from 29,465 stars to 1 star.
A clone detection was then performed between the outdated code snippets and the GitHub
projects. We selected SourcererCC with with the same settings (see \Cref{tab:clone_config}) 
for this task because it could scale to a large-scale data set, while Simian could not. Finally, we analysed
the clone reports and manually checked the clones.

@@

We analysed licensing conflicts of the online clones in the \textbf{QS},
\textbf{EX}, and \textbf{UD} set. The licenses were extracted by \emph{Ninka},
an automatic license identification tool~\cite{German2010}. Since Ninka works at
file level, we report the findings based on Stack Overflow snippets and Qualitas
source files instead of the clone pairs (duplicates were ignored). For the ones
that could not be automatically identified by Ninka and have been reported as
{\small\texttt{SeeFile}} or {\small\texttt{Unknown}}, we looked at them manually
to see if any license can be found. For EX clone pairs that are cloned from
external sources such as JDK or websites, we manually searched for the license
of the original code. Lastly, we searched for occurrences of the license-conflicting
online clones in GitHub projects using the same method as in the outdated clones.

@@

\vspace{0.25cm}
\textit{RQ 1.1 How often are Stack Overflow
	answerers aware of the outdated code and 
	licensing conflicts when
	they answer a question on Stack Overflow?} 
\vspace{0.25cm}

@@

We found that although the answerer have been notified of outdated code in their
answers, for 51.5\% of them such notifications occur very rarely (only 1--20\%
of the answers). Only 3 participants reported that they were notified in more
than 60\% of their answers. This notification to the answerer can be done 
via several means, such as contacting the author directly, 
writing a comment saying that the answer is
already outdated, down-voting the answer or posting a newer answer.
The low percentage of outdated code notifications
reflect the experience of high reputation answerers who accumulate the reputation for a
long time. Due to the voting mechanism of Stack Overflow, high reputation users
usually provide high quality answers to earn up votes from other users. They are
careful when posting code snippets in the answer to avoid problems and, vice versa, 
getting down votes. It would be interesting to compare the findings to
Stack Overflow answerers who are newer and have lower reputation. However, we
leave it to future work.

@@

\begin{boxquote}
	To answer RQ 1.1, although most of the Stack Overflow answerers are aware that their code
	can be outdated, 51.5\% of the answerers were very rarely notified and 35.5\% have never been notified of
	outdated code in the answers. After being notified, 19.8\% of them rarely or never fix the outdated code.
	124 answerers out of 200 (62\%) are aware of Stack Overflow's
	CC BY-SA 3.0 license applied to code snippets in questions and answers. However,
	only 3 answerers explicitly include software license in their answers. Some 
	answerers choose to include the license in their profile page instead. 69\% of the
	answerers never check for licensing conflicts between their copied code snippets
	and Stack Overflow's CC BY-SA 3.0.
%	To answer RQ 1.1, although most of the Stack Overflow answerers are aware that their code
%	can be outdated, half of the answerers were very rarely notified of
%	outdated code in the answers. After being notified, some of them rarely or never fix the outdated code.
%	More than half of the answerers are aware of Stack Overflow's
%	CC BY-SA 3.0 license. Only 3 answerers explicitly include software license in their answers
%	while some of them choose to include the license in their profile page instead. More than half of the
%	answerers never check for licensing conflicts between their copied code snippets
%	and Stack Overflow's CC BY-SA 3.0.
\end{boxquote}

@@

\vspace{0.25cm}
\textit{RQ 1.2 How often do Stack Overflow
	visitors experience the outdated code and licensing conflicts when
	they reuse code in an answer from Stack Overflow?}
\vspace{0.25cm}

@@

\begin{boxquote}
	To answer RQ 1.2, Stack Overflow visitors experienced several issues from Stack
Overflow answers including outdated code. 85\% of them are not aware of
CC BY-SA 3.0 license enforced by Stack Overflow and 66\% never check for license
conflicts when reusing code snippets.
\end{boxquote}

@@

We performed a detailed investigation of the 100 outdated answers on Stack
Overflow two years after the snapshot we have (6 May 2018) 
on three aspects: newer or higher-voted answers and comments. We found
that there were 34 posts which contains newer answers and 5 posts which contained answers with a higher number of
votes than the outdated answers. However, 99 of the 100 outdated answers were still
marked as accepted answers. For the comments, we check if there is any comment
to mitigate or point out the toxicity of the outdated code snippets. We found
that, out of 100 answers, there were 6 answers that had a comment saying the
code in the answer is outdated or containing issues, such as \textit{``spring
	3.1 stuff''}, \textit{``...tried this but having connect exception --
	\texttt{javax.mail.MessagingException}:\textit{ Could not connect to SMTP host:
	\texttt{smtp.gmail.com}, port: 465''}, ``You should add a \texttt{buffer.reset(null, 0, 0);} at the end of the try block to avoid excess heap usage (issue no. HADOOP-11323)''} or \textit{``.. I do not have experience
	with new versions of hibernate for a long time. But previously without clean you
	could receive some unexpected results. So I suggest to try different approaches
	or even check latest documentation''}. The 6 outdated code snippets were still
not fixed, but the comments themselves may help to warn other Stack Overflow
users.

@@

Then, we performed code clone detection between the 100 outdated code snippets and 130,703 GitHub projects.
We found 102 cloned candidates appearing in 68 GitHub projects and manually investigated all
of them. As shown in \Cref{tab:outdated_github}, out of the 102 cloned snippets, there were
13 cloned snippets that matched with themselves because some of the Qualitas
projects also appear on GitHub. For other projects besides the Qualitas
projects, there were 32 cloned snippets that were not exactly the same
(e.g.~they contained additional code modifications made by the projects'
developers or they were copied from another source with a slightly different code).
There were 47 cloned snippets that were exactly the same as the
outdated code snippets, which of 12 were buggy.
Two cloned snippets gave attributions to Stack Overflow. The attributions
pointed to different posts than the ones we found, but containing the same code
in the answers. 32 cloned snippets were very likely to be a file-level
clone from its respective original project (e.g. JFreeChart, JUnit, Log4J,
Hadoop) based on their license header and the Javadoc comments. 
13 cloned snippets did not have any hints or evidence of copying.

Interestingly, we discovered that the buggy version of the
\texttt{humanReadableInt()} method from Hadoop appeared in two popular Java
projects: deeplearning4j (8,830 stars and 4,223 forks) and Apache Hive (1,854
stars and 1,946 forks). Due to the lack of evidence, we could not conclude how
this method, which is exactly the same as the toxic code snippet we found on
Stack Overflow, appears in the two projects. It is possible that the developers
retrieved them from Stack Overflow, other websites, or from Hadoop code base
directly. Nevertheless, we decided to report the developers of the two projects
regarding the issue. We created a bug report for each project (deeplearning4j
\#4694\footnote{deeplearning4j bug report:
	\url{https://github.com/deeplearning4j/deeplearning4j/issues/4692}} and
HIVE-18929\footnote{Apache Hive bug report: \url{
		https://issues.apache.org/jira/browse/HIVE-18929}}) and communicated with the
developers of the projects by describing the problem of race condition in the
outdated version of \texttt{humanReadableInt()} method and proposed a fix by
using the newest version of the method in Hadoop. The issue has been fixed in
deeplearning4j. The developers of deeplearning4j agreed that the method was
problematic and decided to implement their own fix due to a concern of a
potential software licensing conflict caused by copying the fix directly from
Hadoop code base. The bug report in Apache Hive is still
unfixed.

Although we did not find strong evidence of the outdated code snippets in GitHub
projects, it would still be useful if Stack Overflow implements a flagging of
outdated answers. The outdated online code clones cause problems ranging from
uncompilable code (due to modifications and different API usage in the outdated
code) to the introduction of vulnerabilities to the software~\cite{Xia2014}. An
outdated code with a subtle change (e.g.\ \Cref{fig:before-after}) may be copied
and reused without awareness from developers. Moreover, an outdated code with a
defect (e.g.\ a race condition problem in \Cref{fig:before-after_2}) is clearly
harmful to be reused. Although Stack Overflow has a voting mechanism that may
mitigate this issue, the accepted answer may still be used by naive developers
who copy and reuse the outdated code.

\begin{boxquote}
For RQ4, our results show that 66\% (101) of QS clone pairs on Stack
Overflow are outdated. 86 pairs differ from their newest versions by
modifications applied to variable names or method names, added or deleted
statements, to a fully rewritten code with new method signatures. 15~pairs are
dead snippets. 47 outdated code snippets are found in 130,703 GitHub projects
without evidence of copying. Twelve were buggy. Two of them contains a race condition and
are found in popular projects: deeplearning4j and Apache Hive.
\end{boxquote}

@@

%If developers copy and reuse these licensed pieces of code in their projects,
% conflicts may happen without their realisation.
In our study, we reveal another type of toxic code snippets which is software
licensing issues caused by code cloning to Stack Overflow. We found evidence that
153 pieces of code have been copied from Qualitas projects to Stack Overflow as
examples. Another 109 pieces of code are cloned from external sources. Their
status of accepted answers increase their chances of being reused. Even though
most of the Qualitas projects came with a software license, we found that the
license information were frequently missing after the code was copied to Stack
Overflow. The licensing terms on top of source code files are not copied because
usually only a small part of the file was cloned. In overall, we can see that
most of the Stack Overflow snippets do not contain licensing terms while their
clone counterparts in Qualitas projects and external sources do. Since licensing
statement resides on top of a file, the results here are analysed at file level,
not clone fragment, and clone pairs from the same file are merged. 
The summary of licensing information is listed in
\Cref{tab:license_abc}.

@@

The same GitHub study has been done for license-incompatible code snippets. 
We detected clones between the 214
code snippets with their original license missing (86 QS, 78 EX and 50 UD)  and
130,703 GitHub projects using SourcererCC with 80\% similarity threshold.
Opposite to the outdated clones, we discovered a large number
of 7,207 clone pairs. There were 95 pairs from 10 Qualitas projects on
GitHub and 7,112 pairs from 2,427 other projects. From
\Cref{tab:license_github}, the clones were found in highly-starred
projects (29,465 to 10 stars) to 1-star projects.
We found 12 code snippets with attributions to Stack Overflow questions/answers and
6 of them refer to one of our QS or EX clone pairs.
We used the Ninka tool to automatically identify software license of the 7,207 cloned
code snippets. 
Five code snippets did not have license while the originals had Apache-2, GPLv2,
or EPLv1 license. One snippets had AGPLv3 license while the original had Apache-2 license.
Only 995 code snippets in GitHub projects that have the same license
as the originals in Qualitas.

@@

@@

\begin{boxquote}
	For RQ5, we found 214 code snippets on Stack Overflow that
	could potentially violate the license of their original software. The majority of them
	do not contain licensing statements after they have been copied to
	Stack Overflow. For 164 of them, we were able to identify,
	with evidence, where the code snippet has been copied from.
	We found occurrences of 7,112 clones of the 214 license-incompatible code snippets
	in 2,427 GitHub projects.
\end{boxquote}

@@

This study empirically show from the surveys and the clone detection experiment that
online code clones occur on Stack Overflow and the clones may become toxic due
to outdated code and software license incompatibility. The findings lead to the
insight about toxicity of online code clones and we proposed three actionable items
to the software engineering research and the Stack Overflow community.

\subsubsection{Toxicity of outdated and license-incompatible clones}
We found only a small amount of toxic outdated code snippets in open source projects on
GitHub. Besides 12 buggy and outdated code snippets found in 12 projects, the
rest were non-harmful clones of the outdated code. Although other studies show
that Stack Overflow code snippets may become toxic by containing security
vulnerabilities~\cite{Acar2016,Fischer2017} or API misuse~\cite{Zhang2018}, we
found in this study that the damage caused by outdated code on Stack
Overflow is not high.

On the other hand, the missing of licensing statement of online code clones on
Stack Overflow can cause more damage than outdated code. As shown in our study and
also in the study by An et al. \cite{An2017}, some online clones on Stack Overflow are
originally licensed under more restrictive license than Stack Overflow's CC
BY-SA 3.0. If these missing-license online clones are reused in a software with
incompatible license, the software owner may face legal issues. The software
auditing service such as Black Duck Software or nexB, which can effectively
check for license compliance of code copied from open source projects, cannot
check for the original license of the cloned code snippets on Stack Overflow. Although
Stack Overflow answerers participated in our survey believe that most of the
code snippets on Stack Overflow are too small to claim for copyright and they
fall under fair-use, there is still a risk due to different legal system in each
country. For example, Germany legal system does not have a concept of fair use.
In addition, the number of minimum lines of code to be consider copying, i.e.~de minimis,
is also differently interpreted from case to case or from country to country.

@@

While checking if the copied code snippets on Stack Overflow are still
up-to-date with the latest version of their originals can possibly be done
automatically, it is a challenging task to automate the process of establishing
the direction of code cloning as previously discussed. 
Since automatically establishing code cloning direction
is still an open challenge, one viable solution for now is
encouraging the Stack Overflow developers to always include the origin of the
copied code snippet in the post so that this link is always established at the
posting time. Even better, Stack Overflow can provide an optional form to fill
in when an answerer post an answer if he or she copies code from other software
projects. The form should include the origin of the code snippet (possibly as a
GitHub url) and its original license. Using this manually established links at
posting time, we can then automate the process of checking for outdated code.
